Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation

### 2014-11-14 egpaper_final.tex
first draft conclusion
spellcheck exp
added estimation on the title

%%%%%%%%% TITLE
\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

@@

We propose an efficient method for synthesizing templates from 3D models that
runs on the fly -- that is, it quickly produces detectors for an arbitrary
viewpoint of a 3D model without expensive dataset-dependent training or template
storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
method synthesizes a discriminative template by extracting features from a
rendered view of the object and decorrelating spatial dependences among the
features. Our decorrelation procedure relies on a gradient-based algorithm that
is more numerically stable than standard decomposition-based procedures, and we
efficiently search for candidate detections by computing FFT-based template
convolutions. Due to the speed of our template synthesis procedure, we are able
to perform joint optimization on continuous scale, translation, rotation, and
focal length. We provide an efficient GPU implementation of our algorithm, and
we validate its performance on 3DObject dataset and PASCAL 2012 dataset.

@@

\section{Pipeline}
\label{sec:approach}
\input{approach}

@@

\section{Conclusion}

>>>>

%%%%%%%%% TITLE
\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

@@

We propose an efficient method for synthesizing templates from 3D models that
runs on the fly -- that is, it quickly produces detectors for an arbitrary
viewpoint of a 3D model without expensive dataset-dependent training or template
storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
method synthesizes a discriminative template by extracting features from a
rendered view of the object and decorrelating spatial dependences among the
features. Our decorrelation procedure relies on a gradient-based algorithm that
is more numerically stable than standard decomposition-based procedures, and we
efficiently search for candidate detections by computing FFT-based template
convolutions. Due to the speed of our template synthesis procedure, we are able
to perform joint optimization on continuous scale, translation, rotation, and
focal length. We provide an efficient GPU implementation of our algorithm, and
we validate its performance on 3D Object Classes and PASCAL3D+ datasets.

@@

\section{On-the-Fly Template Generation}
\label{sec:approach}
\input{approach}

@@

\section{Conclusion}
\label{conclusion}
\input{conclusion}
